Introducing statistics with `intRo`

### 2016-01-20 jcgs-paper-2016/paper.Rmd
Clean up the output of helper.R

    if (type == "totalpercs") interpolate(~(my.tbl <- my.tbl / 
                                          sum(table(df$y, df$x))), 
                                          df = quote(intro.data), x = x, y = y,  
                                          mydir = userdir, 
                                          `_env` = environment(), 
                                          file = "code_contingency.R", 
                                          append = TRUE)
    if (type == "rowpercs") interpolate(~(my.tbl <- t(apply(
        my.tbl[-nrow(my.tbl),], 1, function(row){row / row[ncol(my.tbl)]}))),  
                                        mydir = userdir,
                                        `_env` = environment(), 
                                        file = "code_contingency.R", 
                                        append = TRUE)
    if (type == "columnpercs") interpolate(~(my.tbl <- apply(
        my.tbl[,-ncol(my.tbl)], 2, function(col){col / col[nrow(my.tbl)]})),  
                                           mydir = userdir, 
                                           `_env` = environment(), 
                                           file = "code_contingency.R", 
                                           append = TRUE)

    if (type %in% c("totalpercs", "rowpercs", "columnpercs")) 
        interpolate(~(new.digits <- digits), 
                    digits = digits, 
                    mydir = userdir,
                    `_env` = environment(), 
                    file = "code_contingency.R", 
                    append = TRUE)
    else interpolate(~(new.digits <- 0),  mydir = userdir, `_env` = environment(), 
                     file = "code_contingency.R", append = TRUE)

@@

This script is most immediately similar to standard R code. In this case, a function `cont.table` is created which, depending on the values of the parameters, ultimately returns a contingency table. One important difference from a typical R script is that each call in the script is wrapped in a function called `interpolate`. `interpolate` both executes the given R code on the server, and also writes the code executed to the script window at the bottom of \texttt{intRo}. More details on the reasons and choices behind `interpolate` can be found in the next section.

>>>>

    # Additional formatting code suppressed for readability
    ...

@@

This script is most immediately similar to standard R code. In this case, a function `cont.table` is created which, depending on the values of the parameters, ultimately returns a contingency table. One important difference from a typical R script is that each call in the script is wrapped in a function called `interpolate`. `interpolate` both executes the given R code on the server, and also writes the code executed to the script window at the bottom of \texttt{intRo}. More details on the reasons and choices behind `interpolate` can be found in section \ref{reproducibility}.
